%% SECTION HEADER /////////////////////////////////////////////////////////////////////////////////////
\section{Structural health monitoring}
\label{sec:scm}

%% SECTION CONTENT ////////////////////////////////////////////////////////////////////////////////////
\Ac{shm} is the process of implementing an advanced damage identification strategy for structural or mechanical systems \cite{farrar2007introduction}.
The \ac{shm} systems usually consist of a sensor network, a \ac{dau}, and a central processor.
The \ac{dau} is responsible for collecting the data measured by the sensor network.
A central unit then determines the current state of the structure through signal processing and statistical classification.
The main goal of \ac{shm} is to increase structure safety use through the ability to observe crucial components in real time.
Since advanced \ac{shm} methods are also applied to structures made of lightweight composite materials, the economic aspect is improved in addition to safety.
For example, composites and adhesive bonding techniques reduce the aircraft's weight and fuel consumption \cite{scelsi2011potential}.
The \ac{shm} is most commonly found in structures, such as aerospace, civil and mechanical engineering, where damage can have catastrophic consequences.

Rytter, in his dissertation \cite{rytter1993vibrational}, classified the \ac{shm} system advancement into the following four levels:
\begin{itemize}
	\item[] \textbf{Level 1}: Detection,
	\item[] \textbf{Level 2}: Localisation,
	\item[] \textbf{Level 3}: Assessment,
	\item[] \textbf{Level 4}: Consequence.
\end{itemize}
The first level determines if any adverse change in the geometry or material characteristics of the system has occurred.
The second level leads to the localisation of the damage.
The two most advanced levels of the system determine the size of the flaw and decide whether any maintenance is necessary, respectively.
The existence and location of faults can be defined in unsupervised learning mode by taking a threshold value for a measurable, damage-sensitive system feature. The threshold should be compensated depending on the prevailing operational and environmental conditions.
In contrast, damage size is determined in supervised learning mode based on an analytical model or data extracted experimentally from the structure \cite{worden2007fundamental, hou2018structural}.