% Note that the text in the [] brackets is the one that will
% appear in the table of contents, whilst the text in the {}
% brackets will appear in the main thesis.

%% CHAPTER HEADER /////////////////////////////////////////////////////////////////////////////////////
\chapter{Formulation of the Time-Domain Spectral Element Method}
\label{ch:sem}
%% CHAPTER INTRODUCTION ///////////////////////////////////////////////////////////////////////////////
The comprehensive formulation of the \ac{sem}-based numerical model is presented in the Chapter.
It includes shape function definition, numerical integration in the scheme of the \ac{gll}, determination of the structural matrices for solid and first-order shear deformation theory elements and electromechanical coupling for the \acp{pzt}.
The non-matching interface was introduced with the novel approach based on the element shape functions.
These components were combined to implement the \ac{sem} for the honeycomb structure with the \ac{fcgm}, which has not been found in the literature before.

%% INCLUDE SECTIONS ///////////////////////////////////////////////////////////////////////////////////
\input{Chapters/Chapter4/sec:sem}
\input{Chapters/Chapter4/sec:2Dmodel}
\input{Chapters/Chapter4/sec:3Dmodel}
\input{Chapters/Chapter4/sec:PZTmodel}
\input{Chapters/Chapter4/sec:damping}
\input{Chapters/Chapter4/sec:interface}
\input{Chapters/Chapter4/sec:transformation}
\input{Chapters/Chapter4/sec:time}
\input{Chapters/Chapter4/sec:gpu}
\input{Chapters/Chapter4/sec:improvement}
\section{Conclusions}
\label{sec:conclusionsSEM}
%% SECTION CONTENT ////////////////////////////////////////////////////////////////////////////////////
The Chapter describes the \ac{sem} implementation for use in \acp{hsc} with the \ac{fcgm}.
This model requires the development of structural matrices for \ac{2d} and \ac{3d} elements and a transformation of the nodal displacements between the local and global coordinate systems.
An original approach was developed to connect elements with non-matching grids using an interface based on Lagrange multipliers.
For this purpose, the shape fusions of common points in the space of connected elements were determined to calculate the traction forces necessary to provide joint displacements.

The implementation of the non-matching interface is a major contribution to the development of the \ac{sem} method.
Previously, to connect domains of different shapes, their meshes were matched with each other to enable the connection of nodes.
Without the interface, connecting the specimen components, i.e. the honeycomb core, the rectangular skin and the circular sensor, would have been extremely difficult.
It would probably require assuming some constraints, such as the sensor being located only within the area of the core cell.
The application of the interface goes beyond the dissertation subject; among other things, it was used in the simulation of \ac{gw} registration by the \ac{fbg} optical sensors.

In addition, a parallel central difference method implementation was improved for even more efficient computation on the graphics card.
The obtained equation of motion solution was even 10 times faster than the algorithm presented in the paper \cite{kudela2020parallel}.

