% Note that the text in the [] brackets is the one that will
% appear in the table of contents, whilst the text in the {}
% brackets will appear in the main thesis.

%% CHAPTER HEADER /////////////////////////////////////////////////////////////////////////////////////
\chapter{Experimental Validation of the Models}
\label{ch:validation}

%% CHAPTER INTRODUCTION ///////////////////////////////////////////////////////////////////////////////
The Chapter includes an assessment of the accuracy and reliability of the modelled physical processes.
In order to validate the sensor model, in the frequency-domain \ac{emi} characteristic was determined through numerical simulations.
The characteristic was then compared with values obtained by theoretical analysis and with experimental measurements.
On the other hand, \ac{hsc} panel model was evaluated experimentally in two ways: by analysing the full wavefield obtained by the \ac{sldv} and by studying the time signals measured by the \acp{pzt} setup.
%% INCLUDE SECTIONS ///////////////////////////////////////////////////////////////////////////////////
\input{Chapters/Chapter6/sec:pztVal}
\input{Chapters/Chapter6/sec:setup}
\input{Chapters/Chapter6/sec:results_sldv}
\input{Chapters/Chapter6/sec:results_pzt}

\section{Conclusions}
\label{sec:conclusionsValid}

%% SECTION CONTENT ////////////////////////////////////////////////////////////////////////////////////
The Chapter presents the validation of the developed models.
The \ac{emi} characteristic of the \ac{pzt} model was in good agreement with analytically obtained characteristic and with experimental results in the analysed frequency range of 0-300 \unit{\kHz}.
The \ac{sldv} analysis showed that \ac{fcgm} expresses better wave propagation behaviour in \ac{hsc} than homogenised model.
The snapshots of the full wavefield showed wave interference in the core cells, which was impossible to obtain in the \ac{hcgm}.
The full-field analysis also showed a lack of wave leakage into the core at the damaged area.
This phenomenon is the basis for determining the effect of the damage on wave propagation.
The velocity of the wave propagation for both models was in good agreement with the \ac{pzt} measurements.