% Note that the text in the [] brackets is the one that will
% appear in the table of contents, whilst the text in the {}
% brackets will appear in the main thesis.

%% CHAPTER HEADER /////////////////////////////////////////////////////////////////////////////////////
\chapter[Parameter study of \ac{gw} propagation in \ac{hsc}]{Parameter study of \ac{gw} propagation in \ac{hsc}}
\label{ch:tempEffects}

%% CHAPTER INTRODUCTION ///////////////////////////////////////////////////////////////////////////////
In the chapter~\ref{ch:severity}, the \ac{madif} was determined for the sample at ambient temperature of \(+20^{\circ}\)C.
However, quasi-stable conditions can only be guaranteed in a laboratory.
Therefore, from a practical point of view, it is necessary to consider changes due to different working conditions.
In this chapter, a study will be carried out to determine the effect of various ambient temperatures on the \ac{madif}.
In addition, a series of computer simulations will be performed to determine how the different parameters of the \ac{hsc} components affect the wave propagation in this structure.
The analysis will include factors such as the adhesive thickness, the \ac{pzt} placement regarding the core cell, the core orientation regarding the wave propagation and volume fraction of reinforcing fibres.
Finally, the \ac{madif} will be developed for \ac{hsc} with the skins on the top and bottom sides of the core.
%% INCLUDE SECTIONS ///////////////////////////////////////////////////////////////////////////////////
\input{Chapters/Chapter8/sec:madifTemp}
\input{Chapters/Chapter8/sec:parameters}
\section{Conclusions}
\label{sec:conclusionsTemp}
This chapter presented a parametric study to obtain temperature-dependent \ac{madif} and determine the influence of various parameters of structural components on \ac{gw} propagation in \ac{hsc}.

The \ac{madif} obtained numerically for different ambient temperatures agree very well with the experimental results, especially for temperatures around the reference one.
The absolute error increases with the higher difference in temperature.
It is probably because the assumed linear model is not sufficient enough.

During the analysis, it was shown that the phenomenon of elastic wave propagation in the \ac{hsc} is very complex, and the amplitude value and velocity of the wave strongly depends on many parameters of individual components, signal excitation and environmental conditions.
In the future, it would be essential to develop an optimisation method to determine the material properties and geometry of the structure in order to fit the model to the monitored sample more accurately.
Such a tool based on a genetic algorithm has been developed for a woven fabric reinforced composites by Kudela et al. \cite{kudela2020elastic}.

Computer simulations were also conducted to determine the \ac{madif} for a double-skin structure.
The function, similar to that of a single-skin panel, satisfies the conditions for damage estimation.