%% CHAPTER HEADER /////////////////////////////////////////////////////////////////////////////////////
\chapter[The Severity of Damage Estimation]{The Severity of Damage Estimation}
\label{ch:severity}

%% CHAPTER INTRODUCTION ///////////////////////////////////////////////////////////////////////////////
A series of computer simulations were performed for different bond sizes for both the \ac{fcgm} and the \ac{hcgm}.
Two damage models were considered i.e., the removed core cells  and no coupling between the core and the adhesive layer.
The electrical voltage signal captured at the sensor was then analysed to determine the \ac{madif}.
Several \acfp{di} were used to determine the effect of damage on the propagation waveform.
Of all the indices, those that were monotonic in the assumed damage size range and with the most significant change in index value were selected for further consideration.
Then, the results were compared with the corresponding indices obtained experimentally.
Finally, those with the lowest error were selected to determine the \ac{madif}.
%% INCLUDE SECTIONS ///////////////////////////////////////////////////////////////////////////////////

\input{Chapters/Chapter7/sec:di}
\input{Chapters/Chapter7/sec:determination}
\clearpage

\section{Conclusions}
\label{sec:conclusionsSever}
In the Chapter, the milestone of the dissertation was achieved in form of determining the \ac{madif}.
For this purpose, six \acp{di} were analysed for two models of the honeycomb core and two models of damage.

Among the indices, the best two \acp{di} were selected to determine the \ac{madif} function.
Their characteristics were monotonic over the entire damage range and a significant change in the index value for the most extensive damage.
The numerical results were in excellent agreement with the experimental measurements.
The \ac{hcgm} proved inadequate for determining the \ac{madif}, as all tested \acp{di} reached a mean error of more than 20\% relative to the experimental measurements.

The analysis demonstrated the confirmation of the thesis that it is possible to determine the damage severity function in \ac{hsc} by employing numerical simulations.
It concerned a rectangular defect between the sensors, so that it can be the basis for further studies with various shapes and locations of damage.