%% CHAPTER HEADER /////////////////////////////////////////////////////////////////////////////////////
\chapter[The Severity of Damage Estimation]{The Severity of Damage Estimation}
\label{ch:severity}

%% CHAPTER INTRODUCTION ///////////////////////////////////////////////////////////////////////////////
A series of computer simulations were performed for different bond sizes for both the \ac{fcgm} and the \ac{hcgm}.
Two damage models were considered, i.e., the removed core cells  and no coupling between the core and the adhesive layer.
The electrical voltage signal captured at the sensor electrode was then analyzed to determine the \ac{madif}.
Several \acfp{di} were used to determine the effect of damage on the propagation waveform.
Of all the indices, those that are monotonic in the assumed damage size range and with the most significant change in index value will be selected for determining the \ac{madif}.
Then, the results are compared with the corresponding indices obtained for experimental measurements.
Lastly, those with the lowest error are chosen for the \ac{madif}.
%% INCLUDE SECTIONS ///////////////////////////////////////////////////////////////////////////////////

\input{Chapters/Chapter7/sec:di}
\input{Chapters/Chapter7/sec:determination}

\section{Conclusions}
\label{sec:conclusionsSever}
In this chapter, the \ac{madif} was determined by which the milestone of the dissertation was achieved.
For this purpose, six \acp{di} were analysed for two different models of the panel core and two models of the damage.

Among the indices, the best two \acp{di} were selected to determine the \ac{madif} function.
Their characteristics are monotonic over the entire damage range and a significant change in the index value for the most extensive damage.
The numerical results are in excellent agreement with the experimental measurements.
The \ac{hcgm} proved inadequate for determining the \ac{madif}, as all tested \acp{di} reached a mean error of more than 20\% relative to the experimental measurements.

The presented analysis demonstrates the confirmation of the thesis that it is possible to determine the damage severity function in \ac{hsc} by employing numerical simulations.
It concerns a rectangular defect between the sensors, so that it can be the basis for further studies with various shapes and positions of damage.